Deployable Probabilistic Programming

### 2019-04-17 paper/paper.tex
more on challenges

>>>>

A flexible data interface is also benefitial for support of
mini-batch optimization~\cite{LZC+14}. Mini-batch optimization
is used when the data set is too big to fit in memory, and the
objective function gradient is estimated based on mini-batches
--- small portions of data. Different models and inference
objectives may require different mini-batch loading schemes.
For best performance of mini-batch optimization, it should be
possible to program loading of mini-batches on case-by-case
basis.
